Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-07-28 document/ms.tex
Some small edits from the Overleaf from GJH
Update the photometry figures
Merge section 2 to a subsection of the old Section 4 (now Section 3)

@@

\subsection{ESPaDOnS Spectroscopy}
We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.  These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.  The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.  In this paper we concentrate on the intensity spectrum.  We apportioned the spectrum into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
\todo{Flux calibration?}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/LkCa4_phot1992-2016.pdf}
	\caption{\name $V-$band photometric monitoring from 1992-2016.}
	\label{fig:PhotTime}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/all_LCs_phase.pdf}
	\caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.  The blue solid lines show a multi-term periodic fit keeping the first $M_{\rm max}=4$ Fourier components.  The vertical lines show the epochs of observations for available spectroscopy.  The unchanged vertical scale highlights the secular drift of the light curve amplitude and morphology.}
	\label{fig:PhotPhase}
\end{figure*}

@@

@@

\begin{table}
\caption{Predicted Photometric Range - based on $V$, adapt for $A_V$}
\label{tab:photrange}
\begin{tabular}{cccc}
\hline
Band & Low Spot & High Spot & Range\\
Cool Spot & 68\% & 83\% &\\
\hline
$B$ & 13.80 & 14.48 & 0.68\\
$V$ & 12.56 & 13.23 & 0.67\\
$R$ & 11.53 & 12.17 & 0.64 \\
$I$ & 10.80 & 11.38 & 0.58\\
$J$ & 9.79 & 10.00 & 0.21\\
$K$ & 8.89 & 9.04 & 0.15\\
\hline
\end{tabular}
\end{table}

>>>>

\subsection{ESPaDOnS Spectroscopy}
We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.  These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.  The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.  In this paper we concentrate on the intensity spectrum.  The spectrum was apportioned into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
\todo{Flux calibration?}

\begin{figure*}
	\centering
	\includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
	\caption{\name $V-$band photometric monitoring from 1992-2016.}
	\label{fig:PhotTime}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/Vband_22s.pdf}
	\caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.  The blue solid lines show a multi-term periodic fit keeping the first $M_{\rm max}=4$ Fourier components.  The vertical lines show the epochs of observations for available spectroscopy.  The unchanged vertical scale highlights the secular drift of the light curve amplitude and morphology.}
	\label{fig:PhotPhase}
\end{figure*}

@@

@@

\begin{figure}
	\centering
    	\vspace{-20mm}
	\includegraphics[width=0.95\textwidth]{figures/phot1_paper} 
    	\vspace{-100mm}
\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
\label{fig:vband_spot}
\end{figure}

@@

\begin{table}
\caption{Predicted Photometric Range}
\label{tab:photrange}
\begin{tabular}{cccc}
\hline
Band & Low Spot & High Spot & Range\\
Cool Spot & 68\% & 83\% &\\
\hline
\multicolumn{4}{c}{Based on $V$, adapt for $A_V$}\\
$B$ & 13.80 & 14.48 & 0.68\\
$V$ & 12.56 & 13.23 & 0.67\\
$R$ & 11.53 & 12.17 & 0.64 \\
$I$ & 10.80 & 11.38 & 0.58\\
$J$ & 9.79 & 10.00 & 0.21\\
$K$ & 8.89 & 9.04 & 0.15\\
\hline
\end{tabular}
\end{table}
